Replication of Gantman et al. 2024

### 2024-03-29 manuscript.qmd
add trailing / for osx compatibility?

```{r}
#| label: Download study 1 data from the OSF
#| include: false
osf_retrieve_node("ngtha") %>%
  osf_ls_files() %>%
  osf_download(path="data/phase_1/final", conflicts="skip")
```

@@

```{r}
#| label: Download the data from the OSF
#| include: false
osf_retrieve_node("x5byq") %>%
  osf_ls_files() %>%
  osf_download(path="data/phase_2/final", conflicts="skip")
```

>>>>

```{r}
#| label: Download study 1 data from the OSF
#| include: false
osf_retrieve_node("ngtha") %>%
  osf_ls_files() %>%
  osf_download(path="data/phase_1/final/", conflicts="skip")
```

@@

```{r}
#| label: Download the data from the OSF
#| include: false
osf_retrieve_node("x5byq") %>%
  osf_ls_files() %>%
  osf_download(path="data/phase_2/final/", conflicts="skip")
```
